Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2019-02-27 paper/snakemajoranas.tex
orders -> order

\comment{We show that zigzag geometry solves this problem by eliminating the long trajectories.}
We propose a new experimental setup (see Fig.~\ref{fig:setup}(b)) for the creation of Majoranas that eliminates long trajectories and therefore prevents the appearance of a soft gap, while also increasing the topological gap by more than an orders of magnitude, depending on the parameters.
The setup consists of a zigzag or snake-like geometry for the semiconductor where long trajectories are not possible due to the geometry.
In this paper we will focus on two-dimensional (2D) Josephson junctions; however, a zigzag geometry will also work with only one superconductor.\footnote{We confirmed this numerically, although it is not included in this paper.}

>>>>

\comment{We show that zigzag geometry solves this problem by eliminating the long trajectories.}
We propose a new experimental setup (see Fig.~\ref{fig:setup}(b)) for the creation of Majoranas that eliminates long trajectories and therefore prevents the appearance of a soft gap, while also increasing the topological gap by more than an order of magnitude, depending on the parameters.
The setup consists of a zigzag or snake-like geometry for the semiconductor where long trajectories are not possible due to the geometry.
In this paper we will focus on two-dimensional (2D) Josephson junctions; however, a zigzag geometry will also work with only one superconductor.\footnote{We confirmed this numerically, although it is not included in this paper.}
